---
title: "FinalProject"
author: "Weige"
date: "12/2/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Access to Twitter API
```{r}
library(devtools)
library(twitteR)

# api_key <- 	"graaQN4SaoDbH4yZXcvcFQ4sN"
# api_secret <- "MveKmYRVelsmX52sqimNAJNIQfWraj6nbK1DS0IxoLuA4cDutp"
# access_token <- "826265114869452800-UeOBS4zqt3gptcoVeWxOLhnHTKTiEvl"
# access_token_secret <- "zSB4cWSZEMQ5ZTNoN0lec8sdArMJrBBiT5Mj2D1tLD01T"
# setup_twitter_oauth(api_key, 
#                     api_secret, 
#                     access_token, 
#                     access_token_secret)
```

Acquire 800 tweets containing "capitalsim" and "communism" respectively from December 6th, 2017 to December 13th, 2017
```{r}
# capdata <- searchTwitter('capitalism', since = '2017-12-6', until = '2017-12-13', lang = "en", n = 5000)
# comdata <- searchTwitter('communism', since = '2017-12-6', until = '2017-12-13', lang = "en", n = 5000)
# capdata <- twListToDF(capdata)
# comdata <- twListToDF(comdata)
```

```{r}
load("FinalShiny/veiger.rdata")
library(tidytext)
library(tidyverse)
library(janeaustenr)
library(stringr)
library(dplyr)
```
text analysis(capitalism) - split the text into seperate words, eliminate stop words and irrelevant words such as "rt", "tweet","http", count the occurance of words and plot the ones that occur more than 120 times in all 5000 tweets
```{r}
tidycap <- capdata %>% 
  dplyr::select(text) %>%
  unnest_tokens(word,text)
data("stop_words")
tidycap <-  tidycap %>% 
  anti_join(stop_words)


tidycap %>%
  count(word, sort = TRUE) %>%
  filter(n>120) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill = "skyblue") +
  xlab(NULL) +
  coord_flip() + ggtitle("Capitalism word frequency")
```

text analysis(communism) - split the text into seperate words, eliminate stop words, count the occurance of words and plot the ones that occur more than 120 times in all 5000 tweets.
```{r}
tidycom <- comdata %>% 
  dplyr::select(text) %>%
  unnest_tokens(word,text)
data("stop_words")
tidycom <-  tidycom %>% 
  anti_join(stop_words)

tidycom %>%
  count(word, sort = TRUE) %>%
  filter(n>120) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill = "pink") +
  xlab(NULL) +
  coord_flip() + ggtitle("Communism word frequency")
```

Compare the words that are frequently used in two sets of data(capitalsim and communism). The more close the word is to the top right, the more frequently it is used in both datasets. 
```{r}
frequency <- bind_rows(mutate(tidycap, ideology = "capitalism"),
                       mutate(tidycom, ideology = "communism")) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(ideology, word) %>%
  group_by(ideology) %>%
  mutate(proportion = n / sum(n)) %>% 
  dplyr::select(-n) %>%
  spread(ideology, proportion) %>%
  gather(ideology, proportion, `communism`)
frequency


library(scales)

ggplot(frequency, aes(x = proportion, y = `capitalism`, color = abs(`capitalism` - proportion))) +
  geom_abline(color = "purple", lty = 2) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.3, height = 0.3) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  scale_color_gradient(limits = c(0, 0.001), low = "purple", high = "darkslategray4") +
  theme(legend.position="none") + ggtitle("Comparison of common words in two groups of tweets") 
```

split the text into lines, set line number as row number, count sentiment scores for each row, and compare the result of two data sets with plots.
```{r}
tidycap2 <- capdata %>% 
  dplyr::select(text) %>%
  mutate(linenumber = row_number()) %>%
  ungroup() %>%
  unnest_tokens(word, text)

tidycom2 <- comdata %>% 
  dplyr::select(text) %>%
  mutate(linenumber = row_number()) %>%
  ungroup() %>%
  unnest_tokens(word, text)


tidycap2 <- tidycap2%>%
  mutate(ideology = "capitalsim")
tidycom2 <- tidycom2%>%
  mutate(ideology = "communism")

com2cap2 <- rbind(tidycap2, tidycom2)

nrcjoy <- get_sentiments("nrc") %>% 
  filter(sentiment == "joy")

nrcjoy

joycap <- com2cap2 %>%
  inner_join(nrcjoy) %>%
  count(word, sort = TRUE)

com2cap2 %>%
  filter(ideology == "capitalism") %>%
  inner_join(nrcjoy) %>%
  count(word, sort = TRUE)

com2cap2 <- com2cap2 %>%
  inner_join(get_sentiments("bing")) %>%
  count(ideology, index = linenumber %/% 30, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)


ggplot(com2cap2, aes(index, sentiment, fill = ideology)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ideology, ncol = 2, scales = "free_x") + ggtitle("A glimpse of sentiment tendency in 2 groups")

```


Select sentimental words in 5000 tweets mentioning "capitalism",plot the top 10 most used positive words and negative words respectively. 
```{r}
capwords <- tidycap %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

capwords %>%
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment",
       x = NULL) +
  coord_flip() + ggtitle("sentiment words in Capitalism")
```

Select sentimental words in 5000 tweets mentioning "communism", plot the top 10 most used positive words and negative words respectively. 
```{r}
comwords <- tidycom %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()


comwords %>%
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment",
       x = NULL) +
  coord_flip() + ggtitle("sentiment words in Communism")
```

wordcloud of mosted used sentimental words in 5000 tweets mentioning "capitalsim", distinguish the negative ones from the positive ones by using different colors. 
```{r}
library(reshape2)
library(wordcloud)

  
  tidycap %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("darkgrey","red"),
                   max.words = 100)
```


wordcloud of mosted used sentimental words in 5000 tweets mentioning"communism", distinguish the negative ones from the positive ones by using different colors. 
```{r}
library(reshape2)

  
  tidycom %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("darkgrey","red"),
                   max.words = 100)
```



#Access to twitter API
```{r}
# library(ROAuth)
# requestURL <- "https://api.twitter.com/oauth/request_token"
# accessURL <- "https://api.twitter.com/oauth/access_token"
# authURL <- "https://api.twitter.com/oauth/authorize"
# consumerKey <- 	"LFNRqX5i1PkB69SjEEncXWloq"
# consumerSecret <- "4sDHqY6aLm7PRfJLxpq6GsWqphZxzX3dXLjssSLXYhO8wPwL3F"
# my_oauth <- OAuthFactory$new(consumerKey = consumerKey, consumerSecret = consumerSecret, 
#                              requestURL = requestURL, accessURL = accessURL, authURL = authURL)
# my_oauth$handshake(cainfo = system.file("CurlSSL", "cacert.pem", package = "RCurl"))
# save(my_oauth, file = "my_oauth.Rdata")
```


Aqcuire tweets sent from the United States that contain "capitalsim" for 20 seconds, plot the map of the United States, and locate these tweets in the map.
```{r}
library(streamR)
# filterStream("tweets_cap.json", track="capitalism", 
#              locations = c(-125, 25, -66,50),  timeout = 30,
#              oauth = my_oauth)   

tweets.cap <- parseTweets("FinalShiny/tweets_cap.json", verbose = TRUE)

library(ggplot2)   
library(grid)   

map.data <- map_data("state")   
cappoints <- data.frame(x = as.numeric(tweets.cap$lon),  
                       y = as.numeric(tweets.cap$lat))

cappoints <- cappoints[cappoints$y > 25, ]   
ggplot(map.data) + 
  geom_map(aes(map_id = region),  
           map = map.data,  
           fill = "white",             
           color = "grey20", size = 0.25) + 
  expand_limits(x = map.data$long, y = map.data$lat) +            
  theme(axis.line = element_blank(),  
        axis.text = element_blank(),  
        axis.ticks = element_blank(),                     
        axis.title = element_blank(),  
        panel.background = element_blank(),  
        panel.border = element_blank(),                     
        panel.grid.major = element_blank(), 
        plot.background = element_blank(),                     
        plot.margin = unit(0 * c( -1.5, -1.5, -1.5, -1.5), "lines")) +  
        geom_point(data = cappoints,             
        aes(x = x, y = y), size = 3,  
        alpha = 1/2, color = "skyblue") + ggtitle("Where did people talk about Capitalism")
```

Aqcuire tweets sent from the United States that contain "communism" for 20 seconds, plot the map of the United States, and locate these tweets in the map.
```{r}
# filterStream("tweets_com.json", track="communism", 
#              locations = c(-125, 25, -66,50),  timeout = 30,
#              oauth = my_oauth)   

tweets.com <- parseTweets("FinalShiny/tweets_com.json", verbose = TRUE)

library(ggplot2)   
library(grid)   

map.data <- map_data("state")   
compoints <- data.frame(x = as.numeric(tweets.com$lon),  
                       y = as.numeric(tweets.com$lat))

compoints <- compoints[compoints$y > 25, ]   
ggplot(map.data) + 
  geom_map(aes(map_id = region),  
           map = map.data,  
           fill = "white",             
           color = "grey20", size = 0.25) + 
  expand_limits(x = map.data$long, y = map.data$lat) +            
  theme(axis.line = element_blank(),  
        axis.text = element_blank(),  
        axis.ticks = element_blank(),                     
        axis.title = element_blank(),  
        panel.background = element_blank(),  
        panel.border = element_blank(),                     
        panel.grid.major = element_blank(), 
        plot.background = element_blank(),                     
        plot.margin = unit(0 * c( -1.5, -1.5, -1.5, -1.5), "lines")) +  
        geom_point(data = compoints,             
        aes(x = x, y = y), size = 3,  
        alpha = 1/2, color = "pink")  + ggtitle("Where did people talk about Communism")
```





